On the properties of discs around accreting brown dwarfs

### 2010-05-27 BD_disc/paper.tex
Latest Version
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@2289 25464f21-6099-402c-b30a-640f1d40d38b

Figure \ref{inner_inc} shows only that for inclinations close to
face-on, the curved inner edge has SEDs with a stronger dependence on
the viewing angle compared to the model with a vertical inner
wall. This leads to a greater dependence of IR colour with
inclination.  Figure \ref{inner_mag} shows the difference in the
inclination dependence of the IR colour for large curved and smaller
vertical inner walls, for the systems shown in Figure \ref{inner_inc}.

\begin{figure*}
  \centering
  \includegraphics[scale=0.6,angle=90]{./Fig/inner_mag.ps}
  \caption{Figure showing the $(J-K)_0$ colour against the
    inclinations of 0, 27, 39, and 48 $^{\circ}$, for the models shown
    in Figure \ref{inner_inc}. The models with the flat, vertical
    inner wall and curved inner edge are shown as the solid and dashed
    lines respectively. The horizontal dotted lines show the change in
    the colour index.\label{inner_mag}}
\end{figure*}

>>>>

Figure \ref{inner_inc} shows only that for inclinations close to
face-on, the curved inner edge has SEDs with a stronger dependence on
the viewing angle compared to the model with a vertical inner
wall. This leads to a greater dependence of IR colour with
inclination.  Figure \ref{inner_mag} shows the difference in the
inclination dependence of the IR colour for large curved and smaller
vertical inner walls (shown as blue and black lines respectively), for
the systems shown in Figure \ref{inner_inc}. The dotted lines are
illustrative of the total change in $(J-K)_0$.

\begin{figure*}
  \centering
  \includegraphics[scale=0.6,angle=90]{./Fig/inner_mag.ps}
  \caption{Figure showing the $(J-K)_0$ colour against the
    inclinations of 0, 27, 39, and 48 $^{\circ}$, for the models shown
    in Figure \ref{inner_inc}. The models with the flat, vertical
    inner wall and curved inner edge are shown as the black and blue
    lines respectively. The horizontal dotted lines show the change in
    the colour index.\label{inner_mag}}
\end{figure*}
